An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0

### 2012-12-18 paper/paper.tex
Add another plot and some description of it

\subsection{SSL-only Asset Combination}
\begin{figure}[h!]
\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_only_ssl_ratio.eps}
\caption{Connection Ratio -- SSL-only Combination Strategy}
\label{fig:combination-ssl}
\end{figure}
The results in Figure \ref{fig:combination-ssl} assume that all assets
described by a mutually-compatible SSL certificate are combined into one SPDY
connection. Two assets have \textit{mutually-compatible} SSL certificates if
their SSL certificates are valid for the host of the other asset (with either
the Canonical Name or the Alternative Hostnames). In this way, we
systematically combine assets by adding them to the largest group with which
they are compatible. We then compare the number of asset groups (SPDY
connections) with the number of assets (HTTP connections). The CDF of the ratio
for the Alexa top 100,000 websites is plotted.

\subsection{SSL-and-IP Asset Combination}
\begin{figure}[h!]
\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_ssl_and_ip_ratio.eps}
\caption{Connection Ratio -- SSL-and-IP Combination Strategy}
\label{fig:combination-ssl-and-ip}
\end{figure}
The results in Figure \ref{fig:combination-ssl-and-ip} assume that all assets
described by a mutually-compatible SSL certificate and that are downloaded from
the same IP in practice are combined into one SPDY connection.
\subsection{Connection Sizes}
% we measure two approaches: splitting on SSL cert and IP and simply splitting
% on SSL cert (as an upper bound for combination). The first method, ssl + ip,
% is prone to some error due to the use of CDNs confusing our scraping of
% assets.

>>>>

\subsection{SSL-only Asset Combination}
\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_only_ssl_ratio.eps}
\caption{Connection Ratio -- SSL-only Combination Strategy}
\label{fig:combination-ssl}
\end{figure}
The results in Figure \ref{fig:combination-ssl} assume that all assets
described by a mutually-compatible SSL certificate are combined into one SPDY
connection. Two assets have \textit{mutually-compatible} SSL certificates if
their SSL certificates are valid for the host of the other asset (with either
the Canonical Name or the Alternative Hostnames). In this way, we
systematically combine assets by adding them to the largest group with which
they are compatible. We then compare the number of asset groups (SPDY
connections) with the number of assets (HTTP connections). The CDF of the ratio
for the Alexa top 100,000 websites is plotted.

\subsection{SSL-and-IP Asset Combination}
\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_ssl_and_ip_ratio.eps}
\caption{Connection Ratio -- SSL-and-IP Combination Strategy}
\label{fig:combination-ssl-and-ip}
\end{figure}
The results in Figure \ref{fig:combination-ssl-and-ip} assume that all assets
described by a mutually-compatible SSL certificate and that are downloaded from
the same IP in practice are combined into one SPDY connection.

\subsection{Connection Sizes}
\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth]{plots/asset_combination_connection_sizes.eps}
\caption{Connection Sizes After Asset Combination}
\label{fig:connection-sizes}
\end{figure}

Figure \ref{fig:connection-sizes} describes the size of connections when all
assets are combined together as described in the SSL-and-IP combination
strategy. 70\% of SPDY connections are noticeably larger than HTTP connections,
up to almost an order of magnitude in some cases. Some assets do not benefit
from SPDY's combination: small assets like Google Analytics tracking
Javascript, or external libraries used on web pages such as jQuery. These
comprise the left part of the SPDY curve.

% we measure two approaches: splitting on SSL cert and IP and simply splitting
% on SSL cert (as an upper bound for combination). The first method, ssl + ip,
% is prone to some error due to the use of CDNs confusing our scraping of
% assets.
